Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
some text about failures of no recomputation.

    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan without recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

    With growing size of the workflow, the excess makespan of not recomputing grows - from $13.9\%$ to $20\%$ for \heftbl,
    from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the 2000-task workflows in this case), $12.1\%$ to $23.5\%$
    for \heftmm.
    The larger variations for \heft can be explained by the small amount of data - for example, there were only 2 200-task
    workflows for this case.

>>>>

    \paragraph{Memory-constrained cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan without recomputation.
    $13$ experiments ended with a valid makespan after recomputation in case of \heft, which corresponds to $4.4\%$ success
    rate. However, there were only $14$ successful \heft experiments overall in this setup, so for the successful experiments
    only, the success rate of not recomputing is $92\%$.
    In case of \heftmm, $16$ experiments ended with a successfully computed makespan without recomputation.
    Because \heftmm managed to schedule all experiments, the rate is $5.5\%$ success without recomputation out of all successful
    schedules with recomputation.
    $50$ experiments were successful in case of \heftblc ($35\%$ out of all successful schedules) and $55$ in case of
    \heftbl (roughly $50\%$ of all successful schedules).

    \heftbl and \heftblc were successful on smaller workflows and failed on larger ones, the success of the strategy without
    recomputation was limited to even the smallest of these smaller workflows.
    So, the strategy without recomputation dfelivered valid makespans (independently of the algorithm) on $56$ original
    workflows with $<100$ tasks, $47$ 200-task ones, $25$ 1000-task ones and $6$ 2000-task ones.

    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    With growing size of the workflow, the excess makespan of not recomputing grows - from $13.9\%$ to $20\%$ for \heftbl,
    from $12.7\%$ to $18.7\%$ on \heftblc (but there is no data for the 2000-task workflows in this case), $12.1\%$ to $23.5\%$
    for \heftmm.
    The larger variations for \heft can be explained by the small amount of data - for example, there were only 2 200-task
    workflows for this case.
